\textbf{ Matching forecast time-scale with ecological process }

### 2019-05-09 doc/manuscript.tex
Added expts to ms

Next steps? Play with parameters to show what controls the rate of transition from temporal to spatial model?

@@

We see a role for new theory and new empirical tests. On the theoretical side, what are the parameters that determine how quickly slow processes
influence dynamics? We can play with our simulation models to provide some qualitative answers: the stronger the selection (at the level of genotype 
or species), the shorter the lifespan of the focal organisms, and the greater the dispersal, the more rapid the shift from the temporal to the spatial model
(should we actually DO these runs?). But providing general, analytical solutions would be difficult, even for our relatively simple models.

@@

>>>>

@@

We see a role for new theory and new empirical tests. On the theoretical side, what are the parameters that determine how quickly slow processes
influence dynamics? We can play with our simulation models to provide some qualitative answers. The effects of some parameters are intuitive: in the community turnover example, increasing the fraction of dispersing individuals causes a more rapid shift in species composition and in model weights (Fig. \ref{fig:dispersal}). But other parameters have less straightforward effects. In the eco-evolutionary model, a potentially important parameter is the temperature tolerance of each genotype. We initially thought that increasing the temperature tolerance might accelerate shifts in genotype frequencies by increasing genotypic diversity within populations, but it had the opposite effect (Fig. \ref{fig:thermal_niche}), probably because it decreased the strength of selection. Other factors to consider  might include organism lifespans, and the magnitude of directional environmental change relative to interannaul variation. While simulation experiments are easy and informative, they cannot provide the generality of analytical theory. Unfortunately, deriving analytical solutions would be difficult, even for our relatively simple models.

@@

\section{Supplementary Figures}

\begin{figure}[tbp]
	\centering
	\includegraphics[width=0.7 \textwidth] {compare_Tsigmas.png}
	\caption{In our eco-evolutionary model, the rate of change in the weight of the temporal forecast (y-axis) depends on the temperature tolerance of genotypes, given by $\sigma_T$ (larger values indicate wider thermal niches). }
	\label{fig:thermal_niche}
\end{figure}

\begin{figure}[tbp]
	\centering
	\includegraphics[width=0.7 \textwidth] {compare_dispersal.png}
	\caption{In our community turnover model, the rate of change in the weight of the temporal forecast (y-axis) depends on fraction of propagules dispersing each time step. }
	\label{fig:dispersal}
\end{figure}
